### 2017-01-16 papers.tex
Adds another papers

\begin{itemize}
    \item Discover potential student groups with similar characteristics and
        reactions to a particular pedagogical strategy;~\cite{ind_008}
    \item Detect students' misuse or game-playing; \TODO{Yet to be explore}
    \item Group students who are hint-driven or failure-driven and find common
        misconceptions that students possess; \TODO{Yet to be explore}
    \item Identify learners with low motivation and find remedial actions to
        lower drop-out rates; \TODO{Yet to be explore}
    \item Predict/classify students when using intelligent tutoring systems;
        \TODO{Yet to be explore}
\end{itemize}

@@

\begin{itemize}
    \item Predicting students' grades from test scores using neural
        networks;~\cite{ind_009}
    \item Predicting student academic success (classes that are successful or
        not) using discriminant function analysis; \TODO{Yet to be explore}
    \item Classifying students using genetic algorithms to predict their final
        grade; \TODO{Yet to be explore}
    \item Predicting a student's academic success (to classify as low, medium
        and high risk classes) using different data mining methods; \TODO{Yet
        to be explore}
    \item Predicting a student’s marks (pass and fail classes) using regression
        techniques in Hellenic Open University data; \TODO{Yet to be explore}
    \item Using neural network models from Moodle logs; \TODO{Yet to be
        explore}
\end{itemize}

@@

>>>>

\begin{itemize}
    \item Discover potential student groups with similar characteristics and
        reactions to a particular pedagogical strategy;~\cite{ind_008}
    \item Detect students' misuse or game-playing; (2)
    \item Group students who are hint-driven or failure-driven and find common
        misconceptions that students possess; (34)
    \item Identify learners with low motivation and find remedial actions to
        lower drop-out rates; (9)
    \item Predict/classify students when using intelligent tutoring systems;
        (16)
\end{itemize}

@@

\begin{itemize}
    \item Predicting students' grades from test scores using neural
        networks;~\cite{ind_009}
    \item Predicting student academic success (classes that are successful or
        not) using discriminant function analysis; (21)
    \item Classifying students using genetic algorithms to predict their final
        grade; (30)
    \item Predicting a student's academic success (to classify as low, medium
        and high risk classes) using different data mining methods; (30)
    \item Predicting a student’s marks (pass and fail classes) using regression
        techniques in Hellenic Open University data; (18)
    \item Using neural network models from Moodle logs; (11)
\end{itemize}

@@

% =============================================================================
\section{\texttt{IND\_011} - Predicting students' marks from Moodle logs using
neural network models}

Paper is~\cite{ind_011}. But found it on Google Scholar while searching for
Moodle Data Mining. This is another paper that uses neural networks
like~\cite{ind_009} did.

Another paper that attempts to predict student's success given their usage of
Moodle. In this case we see the usage of neural networks, as we've seen
in~\cite{ind_009}. Like in~\cite{ind_007, ind_008, ind_003, ind_010}, Moodle
logs are processed alongside final grades in order to build features for
students.  Neural networks are then trained using that data.

The usual information is taken from logs. For example, date and time of access
of Moodle, if a user saw an item, if it wrote somethings in a forum etc. This
data is pre-processed in order to build a dataset. The built dataset for these
experiments is made from entries of 240 students. The trained neural networks
are Radial Basis Functions. They are trained in a few different ways.

It is shown how training a neural network with an incremental hidden layer
algorithm yields a model capable of achieving 80\% of correctly classified
instances. Other ways to train the networks are shown to be very successful
achieving percentages above 70\%.

Not much is known about how the success metric is calculated, or how the
alternative ways to train the network actually work. But they are listed
nonetheless. The paper leaves a few questions opened, namely the usefulness of
the actual study.

Neural networks are presented as a good model to predict students success, and
are shown to be, in fact, a great model for it. Different ways to train a
network are shown and some hints as to how data is pre-processed into useful
datasets are also shown. Even if the paper is short, doesn't go into detail
about certain aspects of the project, and leaves things opened, it is still a
great resource.

Networks networks are once again shown to work in predicting student's success
given their Moodle usage habits.

See reference 7 in this paper about Radial Basis Functions.
